A Deterministic and Terminating Semantics for the Synchronous Programming Language~\CEU

### 2018-02-19 06-appendix.tex
Conserta erro de digitação no apêndice

The syntactic restrictions discussed in Section~\ref{?}, regarding the body
of~$\ceu{\Fin}$ and~$\ceu{\Loop}$ expressions, is formalized by the
following assumptions.

>>>>

The syntactic restrictions discussed in Section~\ref{?}, regarding the body
of~$\ceu{\Fin}$ and~$\ceu{\Loop}$ expressions, are formalized by the
following assumptions.
